Introducing statistics with \\texttt{intRo}

### 2014-12-11 student-paper-competition-2014/paper.Rmd
Limitation of dataset size (further work)

Challenges do exist with regards to the wider adoption of \texttt{intRo}. For instance, we will need to monitor how well the server hosting \texttt{intRo} handles the load of dozens of students performing data analyses at once. If performance issues are encountered, the infrastructure used may need to be expanded to handle current and future load. An unknown quantity will be how feasible it is to increase adoption of \texttt{intRo} across the department, as well as to other universities.

>>>>

Challenges do exist with regards to the wider adoption of \texttt{intRo}. For instance, we will need to monitor how well the server hosting \texttt{intRo} handles the load of dozens of students performing data analyses at once. If performance issues are encountered, the infrastructure used may need to be expanded to handle current and future load. An unknown quantity will be how feasible it is to increase adoption of \texttt{intRo} across the department, as well as to other universities. One limitation of \texttt{intRo} is that uploading a dataset beyond about 30,000 rows tends to be slow. Even once the data is successfully uploaded, the default modules produce results more slowly than with smaller datasets. This is a limitation that should be further investigated if and when \texttt{intRo} sees wider adoption.
